Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-17 paper.tex
acknowledgements

\textcolor{red}{Mention BSD license, INRIA and stuff.}

>>>>

The project is distributed under the simplified BSD license, encouraging
its use in both academic and commercial settings.

The authors and contributors acknowledge active support from INRIA. Past and
present sponsors of the project also include Google -- for funding code
scholarships (\textit{Google Summer of Code}) --, the Python Software Fundation and
Tinyclues -- for funding coding sprints.
